---
title: "toOrdinal 1.1-0.0"
date: "February 21st, 2019"
---

```{r, echo = FALSE}
is_html_output = function() {
  knitr::opts_knit$get("rmarkdown.pandoc.to")=="html"
}
knitr::opts_chunk$set(collapse = TRUE, comment = "", prompt=TRUE, fig.dpi = 96)
if (is_html_output()) {
    options(width=1000)
}
require(toOrdinal, quietly=TRUE)
```


This is 1.1 release of the **toOrdinal** package.  This release includes a new function `toOrdinalDate` that converts calendar dates:

```{r}
toOrdinalDate()
toOrdinalDate("2017-12-25")
```

This release also updates the [web-documentation](https://CenterForAssessment.github.io/toOrdinal) for the package. 

* English: toOrdinal(1) returns '1st'
* German: toOrdinal(1, language="German") returns '1te'
* French: toOrdinal(1, language="French") returns '1re'
* Spanish: toOrdinal(1, language="Spanish") returns '1.er'
* Swedish: toOrdinal(1, language="Swedish") returns '1:a'

See the new [Getting Started Vignette](https://centerforassessment.github.io/toOrdinal/articles/toOrdinal.html) for more information.

Feel free to drop me a line with any comments, feature requests, or ideas. And give us a shout-out Tweet using the Twitter button in the upper right!
